Preliminary stuff

### 2022-11-14 code/process.Rmd
check for variable codeability

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
```

@@

```{r}
library(googledrive)

f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/1UT6KLRujn6iEQ_s01_4yNfFYqc7hAWTpB-t9mdDp0O8/edit#gid=0")
googledrive::drive_download(f, path="raw_data.xlsx", overwrite=T)
d <- readxl::read_xlsx("raw_data.xlsx", skip=2)

@@

```{r}
d_corr <- d |> filter(!status %in% c("missing", "non-experiment")) |> 
  mutate(replicated_instructor_code=as.numeric(replicated_instructor_code)) |> #forcibly convert the ?s to NAs
  filter(!is.na(replicated_instructor_code) & !is.na(replicated_report_code))
corr <- cor.test(d_corr$replicated_instructor_code, d_corr$replicated_report_code, method = 'spearman')

d_corr |> filter(replicated_instructor_code!=replicated_report_code) |> nrow()
d_corr |> filter(replicated_instructor_code==replicated_report_code) |> nrow()

@@

d_es <-  d |> filter(!status %in% c("missing", "non-experiment")) |> 
  rowwise() |> 
  mutate(d_calc_target=fill_es(target_ES_type, target_ES_value, target_N)) |> 
  mutate(d_calc_rep=fill_es(replication_ES_type, replication_ES_value, replication_N)) |> 
  select(target_ES_type, target_ES_value,d_calc_target, replication_ES_type, replication_ES_value, d_calc_rep)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
theme_set(theme_bw())
```

# TODOs
 - will need count of studies excluded for 
 reproducibility / non-exp / missing
 - Fill in ES conversion for non d/SMD/partial eta (and check for correct conversion of those)
 - check & fill on_turk columns

@@

```{r, eval=F}
library(googledrive)

f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/1UT6KLRujn6iEQ_s01_4yNfFYqc7hAWTpB-t9mdDp0O8/edit#gid=0")
googledrive::drive_download(f, path="raw_data.xlsx", overwrite=T)

```{r}
d <- readxl::read_xlsx("raw_data.xlsx", sheet="aligned data", skip=2) |> 
  select(target_lastauthor_year, status, academic_year, subfield, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_test, target_pvalue, target_ES_type, target_ES_value,
         replication_N, replication_test, replication_pvalue, replication_ES_type, replication_ES_value,
         replicated_instructor_code, replicated_report_code)

@@

```{r, message=T}
d_corr <- d |> filter(!status %in% c("missing", "non-experiment")) |> 
  mutate(replicated_instructor_code=as.numeric(replicated_instructor_code)) |> #forcibly convert the ?s to NAs
  filter(!is.na(replicated_instructor_code) & !is.na(replicated_report_code))

corr <- cor.test(d_corr$replicated_instructor_code, d_corr$replicated_report_code, method = 'spearman')

message("Num not match")
d_corr |> filter(replicated_instructor_code!=replicated_report_code) |> nrow()

message("Num match")
d_corr |> filter(replicated_instructor_code==replicated_report_code) |> nrow()

message("distribution of non-matches")

@@

d_es <-  d |> filter(!status %in% c("missing", "non-experiment")) |> 
  rowwise() |> 
  mutate(d_calc_target=fill_es(target_ES_type, target_ES_value, target_N)) |> 
  mutate(d_calc_rep=fill_es(replication_ES_type, replication_ES_value, replication_N))

@@

# Prelim analysis -- Correlation between ES

There's that one ling paper with ES of 10+...

Might want to just hide that point or something instead...

Could weight by precision or something

```{r}

d_es |> ggplot(aes(x=d_calc_target, y=d_calc_rep, color=as.factor(replicated_report_code)))+
  geom_point()+
  #coord_cartesian(xlim=c(0,5), ylim=c(-1,5))+
  geom_abline(slope=1, intercept=0)+
  scale_color_viridis(discrete=T, direction=-1)

d_es |> ggplot(aes(x=d_calc_target, y=d_calc_rep, color=as.factor(replicated_report_code)))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="Replicated?", x="Original SMD", y="Replication SMD")
```

# code vars for models

NOTE: will need to replace replicated_code with the discussion agreed one!!

## demographics

need to code publication year

```{r}
# needs publication year
d_demo <- d_es 
```

## statistics

? will outliers on ratio_ss cause a problem?

```{r}
d_stats <- d_es |> 
  mutate(log_p =log(target_pvalue),
         log_sample =log(target_N),
         ratio_ss = replication_N/target_N,
         change_platform=ifelse(replication_on_turk==target_on_turk,0,1)) |> 
  #this codes 1 if the original was in person, but replication turk/prolific,
  # 0 if they were both on turk/prolific or both in-person (rare, but happens a few times)
  select(replicated_report_code,log_p,log_sample, ratio_ss, change_platform, academic_year, d_calc_target)

summary(d_stats)
```

## closeness

```{r}

# could do with mutate across, but clearer this way?

d_close <- d_es |> 
  mutate(open_data=ifelse(open_data=="yes", 1,0),
         open_mat=ifelse(open_materials=="yes", 1,0),
         stanford=ifelse(stanford_internal=="yes", 1,0)) |> 
  select(open_data, open_mat, stanford, replicated_report_code,
         academic_year)

summary(d_close)
```

## design

will need to recode mixed designs so they can be binarized

```{r}
d_design <- d_es |> 
  mutate(is_within=case_when(
    within_between=="within" ~ 1,
    within_between=="between" ~ 0),
    log_trials=log(repeated_measure),
    log_sample=log(target_N))|> 
  select(is_within, single_vignette,log_trials, log_sample, replicated_report_code, academic_year)

summary(d_design)
```
